---
title       : Diamond Price Prediction in Singapore Dollars (SGD)
subtitle    : Illustrating Prediction with Regression using Shiny
author      : Sanjeev Kumar Maheve
job         : Coursera Datascience Specialization Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## About the Shiny Application

* The project analyzes the diamond data set from the 'UsingR' package
* The data is diamond prices (in Singapore dollars) and diamond weight in carats (standard measure of diamond mass, 0.2 grams). Below is the output of library(UsingR); data(diamond)
```{r, echo=FALSE}
suppressMessages(library(UsingR))
data(diamond)
head(diamond)
```
* The GOAL includes predicting the price of a diamond for the given carat input. Diamond carat weight is the measurement of how much a diamond weighs. A metric "carat" is defined as 200 milligrams.

NOTE - The application may take few seconds to load completely, please wait...

--- .class #id 

## How to use the Application
* Go to https://sanjeevmaheve.shinyapps.io/ddp-project-diamond-price-prediction/ (The applicaton is hosted on the shinyapps.io server)
* The sidebar panel contains slider weiget to choose carat value with step size 0.05
* OR you can also choose any desired carat value by typing into text/drop-down box
* There is an option to enable/disable ggplot which shows/hides "Plot of the diamond data with mass by carats"
* Once the choice is made, the plot shows prediction value derived using linear regression

```{r, echo=TRUE, results='hide'}
# Lets estimate an expected dollar value increase in price for every carat 
# increase in mass of diamond.
fit <- lm(price ~ carat, data = diamond)
computePrice <- function(desiredCaretVal) {
  (coef(fit)[1] + coef(fit)[2] * desiredCaretVal)
}
```

--- .class #id 

## Example Output
* Red and darkblue intersections show the linear regression based prediction output for carat value = 0.25 and 0.31 respectively

```{r, echo=FALSE, fig.width=6, fig.height=6}
suppressMessages(library(ggplot2))
suppressMessages(library(knitr))

# Lets estimate an expected dollar value increase in price for every carat 
# increase in mass of diamond.
fit <- lm(price ~ carat, data = diamond)
computePrice <- function(desiredCaretVal) {
  (coef(fit)[1] + coef(fit)[2] * desiredCaretVal)
}
g = ggplot(diamond, aes(x = carat, y = price))
g = g + xlab("Mass (carats)")
g = g + ylab("Price (SIN $)")
g = g + geom_point(size = 7, colour = "black", alpha=0.5)
g = g + geom_point(size = 5, colour = "blue", alpha=0.2)
g = g + geom_smooth(method = "lm", colour = "black")
g = g + geom_vline(xintercept = 0.25, colour="red")
g = g + geom_hline(yintercept = computePrice(0.25), colour="red")
g = g + geom_vline(xintercept = 0.31, colour="darkblue")
g = g + geom_hline(yintercept = computePrice(0.31), colour="darkblue")
g
```

--- .class #id 

## Reference Link(s)
1. Reproducible Pitch Presentation

   https://github.com/sanjeevmaheve/DevelopingDataProducts/tree/gh-pages
2. My Shiny Application

   https://github.com/sanjeevmaheve/DevelopingDataProducts/tree/gh-pages/ddp-project-diamond-price-prediction


### Thank You